Numerical trajectory patterns of floating macroalgae

### 2021-03-16 thesis_chapter_3.Rmd
additional corrections made.

---
title: 'Numerical trajectory patterns of floating macroalgae'
author:
- R Coppin^[University of the Western Cape]
- C Rautenbach^[South African Weather Service]
- AJ Smit^[University of the Western Cape]
output:
  word_document:
    reference_docx: markdown/frontiers_template.docx
  html_document:
  pdf_document:
    fig_caption: yes
    latex_engine: xelatex
bibliography: references.bib
csl: markdown/frontiers.csl.txt
abstract: The ocean currents act as an important dispersal mechanism of material on the ocean surface, both natural and anthropogenic. Macroalage are one of the most important natural dispersal mechanisms in the ocean, and are regarded as the tumble-weed of the ocean. Despite the many studies that exist, the relative role of wind and surface currents in macrolage trajectory is still unknown. Past studies also tend to focus on kelp-rafts which can vary greatly in size and making it difficult to form a concensus as to the role of wind and surface currents. In addition past studies have not conisidered surface-area in relation to drag characterisics of floating macroalgae, which have been shown to play a role in the trajectory and accumulation of other flotsam. The advances in Lagrangian trajectory modeling has been exponential in recent years and allows the use of numerical experiments to investigate trajectory of flotsam in the ocean. This study aimed to shed light on the relative role of wind versus surface currents, as well as the role of drag, in macrolagae trajectory and accumulation. This study did not investigate kelp-raft behaviour but instead focused on solitary kelp individuals. This was achieved by comparing simulations of virtual kelp particles which incorporate drag with that of purley Lagrangian particles. The results showed that the virtual kelp particles do follow the ocean currents in general, but that the inclusion of drag into the scnearios causes accumulation in eddies and vortices within the study domain. The results also point to the importance of sub-mesoscale features, such as eddies and vortices, as important surface accumlation zones for solitary floating macroalage.
---

@@

The region of interest for this study was the Cape Peninsula in the Western Cape (Figure 1A). A release site was chosen for this study, Kommetjie, which is located on the Atlantic side of the Cape Peninsula (Figure 2B). The hydrodynamics in the study region are driven by a complex interaction of wind and waves, which are also influenced by larger oceanic processes. In South Africa, the larger processes can be attributed to the Agulhas Current (AC) and the Benguela Current (BC)[@lutjeharms2000;@lutjeharms2007;@garzoli1996;@Hutchings2009;@rubio2009]. The AC is a component of the South-west Indian Ocean sub-gyre, flowing predominantly south-westward following the continental shelf edge and eventually retroflecting eastward back into the South Indian Ocean [@lutjeharms2000;@lutjeharms2007]. The region where the retroflection occurs is known as the Agulhas Retroflection and consists of high levels of mesoscale variability [@garzoli1996]. The variability results in shedding of rings and filaments known as the Agulhas Rings and have an average diameter of ~324km [@lutjeharms1988; @lutjeharms2006; @lutjeharms2007]. The Agulhas Rings are the main contributors to the Agulhas leakage which are the transport of warm water from the Indian Ocean to the South Atlantic Ocean [@garzoli1996; @lutjeharms2006; @beal2015]. The Agulhas leakage is also a source of meso-scale variability within the Benguela region as anticyclonic rings are shed and drift northwestward along the southern Benguela slope region [@rubio2009]. The Benguela region is characterised by strong coastal upwelling cells which are primarily driven by equatorward winds [@shannon1996; @hardman2003]. It is known as the Benguela Upwelling System (BUS) The BUS starts at 27$^\circ$S and extends southward to 35$^\circ$S [@shannon1996]. The region is also characterised by high amounts of mesoscale variability in the form of eddies and filaments [@blanke2002; @blanke2005; @rubio2009]. The Benguela inshore region is dominated by a northwestward flow because of topographical steering, wind stress and interactions with passing Agulhas Rings and eddies [@veitch2010].

@@

The study domain falls within the southern Benguela upwelling ecosystem, which is a region of high mesoscale variability and activity. These occur mostly in the form of eddies, filaments and vortices which are generated from the Agulhas retroflection [@veitch2018; @veitch2017], generally flowing northward along the coastline and begin to move offshore near Cape Columbine. The Benguela Jet is a coastal flowing current and is driven by a complex interaction of eddies, upwelling, eckman transport and geostrophic currents [@stramma1989; @veitch2017; @veitch2018; @hutchings2009]. The stability of the jet varies seasonally with more stable flows in winter and splitting of the jet during summer and spring. In January, the jet begins to split between Cape Point and Cape Columbine [@veitch2018; @blanke2005; @blanke2002] which results into a weak narrow inshore branch which flows along the shelf edge and a strong flowing north-westwards offshore branch. The area is also an area of high upwelling activity driven by strong westerly winds [@hutchings2009]. These winds are most intense during summer (December-March) which favours upwelling conditions in the region, and also act to reinforce the flow of the Benguela Jet; which occurs due to cold upwelling waters contributing to the across-shore density gradient [@ragoasha2019]. In winter the wind direction is reversed which decreases upwelling favorable conditions, but the core of the Benguela jet is maintained by the intrusion of warm agulhas waters into the Benguela region over the shelf edge [@veitch2018; @hutchings2009; @ragoasha2019].   
## Particle tracking model

@@

waterdrag_plot <- ggplot()+
  geom_path(data = p_RK4_mean, aes(x = lon, y = lat), color = 'black')+
  geom_path(data = Mean_Kfloat_H100_W00_mean, aes(x = lon, y = lat), color = 'blue')+
  geom_path(data = Mean_Kfloat_H100_W00_mean, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Max_Kfloat_H100_W00_mean, aes(x = lon, y = lat), color = 'red')+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot <- ggplot()+
  geom_path(data = p_RK4_mean, aes(x = lon, y = lat), color = 'black')+
  geom_path(data = Min_Kfloat_H095_W05_mean, aes(x = lon, y = lat), color = 'grey')+
  geom_path(data = Min_Kfloat_H090_W10_mean, aes(x = lon, y = lat), color = 'green')+
  geom_path(data = Min_Kfloat_H085_W15_mean, aes(x = lon, y = lat), color = 'pink')+
  geom_path(data = Mean_KFloat_H095_W05_mean, aes(x = lon, y = lat), color = 'yellow')+
  geom_path(data = Mean_KFloat_H090_W10_mean, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Mean_KFloat_H085_W15_mean, aes(x = lon, y = lat), color = 'red')+
  geom_path(data = Max_Kfloat_H095_W05_mean, aes(x = lon, y = lat), color = 'blue')+
  geom_path(data = Max_Kfloat_H090_W10_mean, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Max_Kfloat_H085_W15_mean, aes(x = lon, y = lat), color = 'red')+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

```{r accumulation data outputs, warning=FALSE, echo=FALSE, message=FALSE, fig.cap="Figure 6: Comparison of trajectory data between passive and kelp accumulation scenarios. Panel A are a comparison of density plots  and panel B is a comparison of age.", fig.height=8, fig.width=8}

@@

## Additional simulations

@@

@@

waterdrag_plot_July <- ggplot()+
  geom_path(data = p_RK4_mean_July, aes(x = lon, y = lat), color = 'black')+
  geom_path(data = Mean_Kfloat_H100_W00_mean_July, aes(x = lon, y = lat), color = 'blue')+
  geom_path(data = Mean_Kfloat_H100_W00_mean_July, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Max_Kfloat_H100_W00_mean_July, aes(x = lon, y = lat), color = 'red')+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot_July <- ggplot()+
  geom_path(data = p_RK4_mean_July, aes(x = lon, y = lat), color = 'black')+
  geom_path(data = Min_Kfloat_H095_W05_mean_July, aes(x = lon, y = lat), color = 'grey')+
  geom_path(data = Min_Kfloat_H090_W10_mean_July, aes(x = lon, y = lat), color = 'green')+
  geom_path(data = Min_Kfloat_H085_W15_mean_July, aes(x = lon, y = lat), color = 'pink')+
  geom_path(data = Mean_KFloat_H095_W05_mean_July, aes(x = lon, y = lat), color = 'yellow')+
  geom_path(data = Mean_KFloat_H090_W10_mean_July, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Mean_KFloat_H085_W15_mean_July, aes(x = lon, y = lat), color = 'red')+
  geom_path(data = Max_Kfloat_H095_W05_mean_July, aes(x = lon, y = lat), color = 'blue')+
  geom_path(data = Max_Kfloat_H090_W10_mean_July, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Max_Kfloat_H085_W15_mean_July, aes(x = lon, y = lat), color = 'red')+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

waterdrag_plot_Oct <- ggplot()+
  geom_path(data = p_RK4_mean_Oct, aes(x = lon, y = lat), color = 'black')+
  geom_path(data = Mean_Kfloat_H100_W00_mean_Oct, aes(x = lon, y = lat), color = 'blue')+
  geom_path(data = Mean_Kfloat_H100_W00_mean_Oct, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Max_Kfloat_H100_W00_mean_Oct, aes(x = lon, y = lat), color = 'red')+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot_Oct <- ggplot()+
  geom_path(data = p_RK4_mean_Oct, aes(x = lon, y = lat), color = 'black')+
  geom_path(data = Min_Kfloat_H095_W05_mean_Oct, aes(x = lon, y = lat), color = 'grey')+
  geom_path(data = Min_Kfloat_H090_W10_mean_Oct, aes(x = lon, y = lat), color = 'green')+
  geom_path(data = Min_Kfloat_H085_W15_mean_Oct, aes(x = lon, y = lat), color = 'pink')+
  geom_path(data = Mean_KFloat_H095_W05_mean_Oct, aes(x = lon, y = lat), color = 'yellow')+
  geom_path(data = Mean_KFloat_H090_W10_mean_Oct, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Mean_KFloat_H085_W15_mean_Oct, aes(x = lon, y = lat), color = 'red')+
  geom_path(data = Max_Kfloat_H095_W05_mean_Oct, aes(x = lon, y = lat), color = 'blue')+
  geom_path(data = Max_Kfloat_H090_W10_mean_Oct, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Max_Kfloat_H085_W15_mean_Oct, aes(x = lon, y = lat), color = 'red')+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=4, fig.width=7, fig.cap="Figure ??: Comparison of mean trajectories. Plot A is the comparison of mean trajectories for only hydrodynamic drag and plot B is the comparison of mean trajectories for simulations with varying degrees of hydrodynamic and wind drag. In plot A, the black line represents simulation 1, the blue line 2, the orange line 6 and the red line 10. In plot B, the black line represents simulation 1, the grey line simulation 3, the green 4, the pink 5, the yellow 7, orange 8, red 9, blue 11, bronze 12, and cherry 13. The reader is referred to tables 1 and 2 for details pertaining to each scenario."}

@@

@@

heatmap_RK4_July <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = p_RK4_July, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "gradient", limits = c(1, 13000)) +
  geom_path(data = p_RK4_mean_July,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("1") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

@@

heatmap_RK4_Oct <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = p_RK4_Oct, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "gradient", limits = c(1, 13000)) +
  geom_path(data = p_RK4_mean_Oct,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("1") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

@@

## Density comparison
### July

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Figure ??: Comparison of density plots at the end run time of each scenario for July 2018 (winter). The plots are regular hexagons within the density of particles is calculated. Plots A-D represents the minimum, plots E-H are the mean and plots I-L the maximum cross-sectional areas. The bottom plot is the density plot for the passive simulation. The mean trajectories for each scenario are also plotted for comparison. The reader is referred to tables 1 and 2 for details pertaining to each scenario.', fig.height=10.2, fig.width=7.5}

figure_a_July <- ggarrange(heatmap_Min_Kfloat_H100_W00_July, heatmap_Min_Kfloat_H095_W05_July,heatmap_Min_Kfloat_H090_W10_July,heatmap_Min_Kfloat_H085_W15_July, heatmap_Mean_Kfloat_H100_W00_July, heatmap_Mean_KFloat_H095_W05_July, heatmap_Mean_KFloat_H090_W10_July, heatmap_Mean_KFloat_H085_W15_July, heatmap_Max_KFloat_H100_W00_July,heatmap_Max_KFloat_H095_W05_July, heatmap_Max_KFloat_H090_W10_July, heatmap_Max_KFloat_H085_W15_July, labels = c("2","3","4","5","6","7","8","9","10","11","12","13"), common.legend = TRUE, legend = c("none"))

@@

```
### October

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Figure ??: Comparison of density plots at the end run time of each scenario for October 2018 (spring). The plots are regular hexagons within the density of particles is calculated. Plots A-D represents the minimum, plots E-H are the mean and plots I-L the maximum cross-sectional areas. The bottom plot is the density plot for the passive simulation. The mean trajectories for each scenario are also plotted for comparison. The reader is referred to tables 1 and 2 for details pertaining to each scenario.', fig.height=10.2, fig.width=7.5}

figure_a_Oct <- ggarrange(heatmap_Min_Kfloat_H100_W00_Oct, heatmap_Min_Kfloat_H095_W05_Oct,heatmap_Min_Kfloat_H090_W10_Oct,heatmap_Min_Kfloat_H085_W15_Oct, heatmap_Mean_Kfloat_H100_W00_Oct, heatmap_Mean_KFloat_H095_W05_Oct, heatmap_Max_KFloat_H090_W10_Oct, heatmap_Mean_KFloat_H085_W15_Oct, heatmap_Max_KFloat_H100_W00_Oct,heatmap_Max_KFloat_H095_W05_Oct, heatmap_Max_KFloat_H090_W10_Oct, heatmap_Max_KFloat_H085_W15_Oct, labels = c("2","3","4","5","6","7","8","9","10","11","12","13"), common.legend = TRUE, legend = c("none"))

@@

```{r distance plot processing additional, message=FALSE, warning=FALSE, include=FALSE, fig.height=3, fig.width=4}
## July

@@

custom_labs_July <- c("1","2", "3", "4", "5", "7", "8", "9", "10", "11", "12", "13") #create custom labels and add them to dis_plot

@@

custom_labs_Oct <- c("1","2", "3", "4", "5", "7", "8", "9", "10", "11", "12", "13") #create custom labels and add them to dis_plot

@@

```{r distance plot additional, message=FALSE, warning=FALSE, echo=FALSE, fig.cap="Figure 4: Boxplots of total distance travelled by all particles from the release site over the course of the simulation for each scenario for July (winter) and October (spring). The x-axis represents the scenario number and the y-axis is the distance travelled in kilometers. The lower and upper hinges correspond to the first and third quartiles. The whiskers represent the range, solid black lines represent the median and black dots are outliers. The reader is referred to tables 1 and 2 for details pertaining to each scenario."}

>>>>

---
title: 'Numerical trajectory patterns of floating macroalgae'
author:
- R Coppin^[University of the Western Cape], C Rautenbach^[National Institute of Water and Atmospheric Research], AJ Smit^[University of the Western Cape]
output:
  word_document:
    reference_docx: markdown/frontiers_template.docx
  html_document:
  pdf_document:
    fig_caption: yes
    latex_engine: xelatex
bibliography: references.bib
csl: markdown/frontiers.csl.txt
abstract: "*Abstract* The ocean currents act as an important dispersal mechanism of material on the ocean surface, both natural and anthropogenic. Macroalage are one of the most important natural dispersal mechanisms in the ocean, and are regarded as the tumble-weed of the ocean. Despite the many studies that exist, the relative role of wind and surface currents in macrolage trajectory is still unknown. Past studies also tend to focus on kelp-rafts which can vary greatly in size and making it difficult to form a concensus as to the role of wind and surface currents. In addition past studies have not conisidered surface-area in relation to drag characterisics of floating macroalgae, which have been shown to play a role in the trajectory and accumulation of other flotsam. The advances in Lagrangian trajectory modeling has been exponential in recent years and allows the use of numerical experiments to investigate trajectory of flotsam in the ocean. This study aimed to shed light on the relative role of wind versus surface currents, as well as the role of drag, in macrolagae trajectory and accumulation. This study did not investigate kelp-raft behaviour but instead focused on solitary kelp individuals. This was achieved by comparing simulations of virtual kelp particles which incorporate drag with that of purley Lagrangian particles. The results showed that the virtual kelp particles do follow the ocean currents in general, but that the inclusion of drag into the scnearios causes accumulation in eddies and vortices within the study domain. The results also point to the importance of sub-mesoscale features, such as eddies and vortices, as important surface accumlation zones for solitary floating macroalage."
---

@@

The region of interest for this study was the Cape Peninsula in the Western Cape (Figure 1A). A release site was chosen for this study, Kommetjie, which is located on the Atlantic side of the Cape Peninsula (Figure 2B). The hydrodynamics in the study region are driven by a complex interaction of wind and waves, which are also influenced by larger oceanic processes. In South Africa, the larger processes can be attributed to the Agulhas Current (AC) and the Benguela Current (BC)[@lutjeharms2000; @lutjeharms2007 ;@garzoli1996 ;@hutchings2009; @rubio2009]. The AC is a component of the South-west Indian Ocean sub-gyre, flowing predominantly south-westward following the continental shelf edge and eventually retroflecting eastward back into the South Indian Ocean [@lutjeharms2000;@lutjeharms2007]. The region where the retroflection occurs is known as the Agulhas Retroflection and consists of high levels of mesoscale variability [@garzoli1996]. The variability results in shedding of rings and filaments known as the Agulhas Rings and have an average diameter of ~324km [@lutjeharms1988; @lutjeharms2006; @lutjeharms2007]. The Agulhas Rings are the main contributors to the Agulhas leakage which are the transport of warm water from the Indian Ocean to the South Atlantic Ocean [@garzoli1996; @lutjeharms2006; @beal2015]. The Agulhas leakage is also a source of meso-scale variability within the Benguela region as anticyclonic rings are shed and drift northwestward along the southern Benguela slope region [@rubio2009]. The Benguela region is characterised by strong coastal upwelling cells which are primarily driven by equatorward winds [@shannon1996; @hardman2003]. It is known as the Benguela Upwelling System (BUS) The BUS starts at 27$^\circ$S and extends southward to 35$^\circ$S [@shannon1996]. The region is also characterised by high amounts of mesoscale variability in the form of eddies and filaments [@blanke2002; @blanke2005; @rubio2009]. The Benguela inshore region is dominated by a northwestward flow because of topographical steering, wind stress and interactions with passing Agulhas Rings and eddies [@veitch2010].

@@

The study domain falls within the southern Benguela upwelling ecosystem, which is a region of high mesoscale variability and activity. These occur mostly in the form of eddies, filaments and vortices which are generated from the Agulhas retroflection [@veitch2018; @veitch2017], generally flowing northward along the coastline and begin to move offshore near Cape Columbine. The Benguela Jet is a coastal flowing current and is driven by a complex interaction of eddies, upwelling, eckman transport and geostrophic currents [@stramma1989; @veitch2017; @veitch2018; @hutchings2009]. The stability of the jet varies seasonally with more stable flows in winter and splitting of the jet during summer and spring. In January, the jet begins to split between Cape Point and Cape Columbine [@veitch2018; @blanke2005; @blanke2002] which results into a weak narrow inshore branch which flows along the shelf edge and a strong flowing north-westwards offshore branch. The area is also an area of high upwelling activity driven by strong westerly winds [@hutchings2009]. These winds are most intense during summer (December-March) which favours upwelling conditions in the region, and also act to reinforce the flow of the Benguela Jet; which occurs due to cold upwelling waters contributing to the across-shore density gradient [@ragoasha2019]. In winter the wind direction is reversed which decreases upwelling favorable conditions, but the core of the Benguela jet is maintained by the intrusion of warm agulhas waters into the Benguela region over the shelf edge [@veitch2018; @hutchings2009; @ragoasha2019].

## Particle tracking model

@@

waterdrag_plot <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black", fill = NA) +
  geom_path(data = p_RK4_mean, aes(x = lon, y = lat), color = 'black')+
  geom_path(data = Mean_Kfloat_H100_W00_mean, aes(x = lon, y = lat), color = 'blue')+
  geom_path(data = Mean_Kfloat_H100_W00_mean, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Max_Kfloat_H100_W00_mean, aes(x = lon, y = lat), color = 'red')+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black", fill = NA) +
  geom_path(data = p_RK4_mean, aes(x = lon, y = lat), color = 'black')+
  geom_path(data = Min_Kfloat_H095_W05_mean, aes(x = lon, y = lat), color = 'grey')+
  geom_path(data = Min_Kfloat_H090_W10_mean, aes(x = lon, y = lat), color = 'green')+
  geom_path(data = Min_Kfloat_H085_W15_mean, aes(x = lon, y = lat), color = 'pink')+
  geom_path(data = Mean_KFloat_H095_W05_mean, aes(x = lon, y = lat), color = 'yellow')+
  geom_path(data = Mean_KFloat_H090_W10_mean, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Mean_KFloat_H085_W15_mean, aes(x = lon, y = lat), color = 'red')+
  geom_path(data = Max_Kfloat_H095_W05_mean, aes(x = lon, y = lat), color = 'blue')+
  geom_path(data = Max_Kfloat_H090_W10_mean, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Max_Kfloat_H085_W15_mean, aes(x = lon, y = lat), color = 'red')+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

```{r accumulation data outputs, warning=FALSE, echo=FALSE, message=FALSE, fig.cap="Figure 5: Comparison of trajectory data between passive and kelp accumulation scenarios. Panel A are a comparison of density plots  and panel B is a comparison of age.", fig.height=8, fig.width=8}

@@

## Additional comparisons

@@

### Comparison of mean trajectories

@@

waterdrag_plot_July <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black", fill = NA) +
  geom_path(data = p_RK4_mean_July, aes(x = lon, y = lat), color = 'black')+
  geom_path(data = Mean_Kfloat_H100_W00_mean_July, aes(x = lon, y = lat), color = 'blue')+
  geom_path(data = Mean_Kfloat_H100_W00_mean_July, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Max_Kfloat_H100_W00_mean_July, aes(x = lon, y = lat), color = 'red')+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot_July <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black", fill = NA) +
  geom_path(data = p_RK4_mean_July, aes(x = lon, y = lat), color = 'black')+
  geom_path(data = Min_Kfloat_H095_W05_mean_July, aes(x = lon, y = lat), color = 'grey')+
  geom_path(data = Min_Kfloat_H090_W10_mean_July, aes(x = lon, y = lat), color = 'green')+
  geom_path(data = Min_Kfloat_H085_W15_mean_July, aes(x = lon, y = lat), color = 'pink')+
  geom_path(data = Mean_KFloat_H095_W05_mean_July, aes(x = lon, y = lat), color = 'yellow')+
  geom_path(data = Mean_KFloat_H090_W10_mean_July, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Mean_KFloat_H085_W15_mean_July, aes(x = lon, y = lat), color = 'red')+
  geom_path(data = Max_Kfloat_H095_W05_mean_July, aes(x = lon, y = lat), color = 'blue')+
  geom_path(data = Max_Kfloat_H090_W10_mean_July, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Max_Kfloat_H085_W15_mean_July, aes(x = lon, y = lat), color = 'red')+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

waterdrag_plot_Oct <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black", fill = NA) +
  geom_path(data = p_RK4_mean_Oct, aes(x = lon, y = lat), color = 'black')+
  geom_path(data = Mean_Kfloat_H100_W00_mean_Oct, aes(x = lon, y = lat), color = 'blue')+
  geom_path(data = Mean_Kfloat_H100_W00_mean_Oct, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Max_Kfloat_H100_W00_mean_Oct, aes(x = lon, y = lat), color = 'red')+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot_Oct <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black", fill = NA) +
  geom_path(data = p_RK4_mean_Oct, aes(x = lon, y = lat), color = 'black')+
  geom_path(data = Min_Kfloat_H095_W05_mean_Oct, aes(x = lon, y = lat), color = 'grey')+
  geom_path(data = Min_Kfloat_H090_W10_mean_Oct, aes(x = lon, y = lat), color = 'green')+
  geom_path(data = Min_Kfloat_H085_W15_mean_Oct, aes(x = lon, y = lat), color = 'pink')+
  geom_path(data = Mean_KFloat_H095_W05_mean_Oct, aes(x = lon, y = lat), color = 'yellow')+
  geom_path(data = Mean_KFloat_H090_W10_mean_Oct, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Mean_KFloat_H085_W15_mean_Oct, aes(x = lon, y = lat), color = 'red')+
  geom_path(data = Max_Kfloat_H095_W05_mean_Oct, aes(x = lon, y = lat), color = 'blue')+
  geom_path(data = Max_Kfloat_H090_W10_mean_Oct, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Max_Kfloat_H085_W15_mean_Oct, aes(x = lon, y = lat), color = 'red')+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=4, fig.width=7, fig.cap="Figure 7: Comparison of mean trajectories. Plot A is the comparison of mean trajectories for only hydrodynamic drag and plot B is the comparison of mean trajectories for simulations with varying degrees of hydrodynamic and wind drag. In plot A, the black line represents simulation 1, the blue line 2, the orange line 6 and the red line 10. In plot B, the black line represents simulation 1, the grey line simulation 3, the green 4, the pink 5, the yellow 7, orange 8, red 9, blue 11, bronze 12, and cherry 13. The reader is referred to tables 1 and 2 for details pertaining to each scenario."}

@@

### Comparison of density

@@

heatmap_RK4_July <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = p_RK4_July, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "gradient", limits = c(1, 13000)) +
  geom_path(data = p_RK4_mean_July,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("30") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

@@

heatmap_RK4_Oct <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = p_RK4_Oct, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "gradient", limits = c(1, 13000)) +
  geom_path(data = p_RK4_mean_Oct,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("43") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Figure 8: Comparison of density plots at the end run time of each scenario for July 2018 (winter). The plots are regular hexagons within the density of particles is calculated. Plots A-D represents the minimum, plots E-H are the mean and plots I-L the maximum cross-sectional areas. The bottom plot is the density plot for the passive simulation. The mean trajectories for each scenario are also plotted for comparison. The reader is referred to tables 1 and 2 for details pertaining to each scenario.', fig.height=10.2, fig.width=7.5}

figure_a_July <- ggarrange(heatmap_Min_Kfloat_H100_W00_July, heatmap_Min_Kfloat_H095_W05_July,heatmap_Min_Kfloat_H090_W10_July,heatmap_Min_Kfloat_H085_W15_July, heatmap_Mean_Kfloat_H100_W00_July, heatmap_Mean_KFloat_H095_W05_July, heatmap_Mean_KFloat_H090_W10_July, heatmap_Mean_KFloat_H085_W15_July, heatmap_Max_KFloat_H100_W00_July,heatmap_Max_KFloat_H095_W05_July, heatmap_Max_KFloat_H090_W10_July, heatmap_Max_KFloat_H085_W15_July, labels = c("32","33","34","35","36","37","338","39","40","41","42","43"), common.legend = TRUE, legend = c("none"))

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Figure 9: Comparison of density plots at the end run time of each scenario for October 2018 (spring). The plots are regular hexagons within the density of particles is calculated. Plots A-D represents the minimum, plots E-H are the mean and plots I-L the maximum cross-sectional areas. The bottom plot is the density plot for the passive simulation. The mean trajectories for each scenario are also plotted for comparison. The reader is referred to tables 1 and 2 for details pertaining to each scenario.', fig.height=10.2, fig.width=7.5}

figure_a_Oct <- ggarrange(heatmap_Min_Kfloat_H100_W00_Oct, heatmap_Min_Kfloat_H095_W05_Oct,heatmap_Min_Kfloat_H090_W10_Oct,heatmap_Min_Kfloat_H085_W15_Oct, heatmap_Mean_Kfloat_H100_W00_Oct, heatmap_Mean_KFloat_H095_W05_Oct, heatmap_Max_KFloat_H090_W10_Oct, heatmap_Mean_KFloat_H085_W15_Oct, heatmap_Max_KFloat_H100_W00_Oct,heatmap_Max_KFloat_H095_W05_Oct, heatmap_Max_KFloat_H090_W10_Oct, heatmap_Max_KFloat_H085_W15_Oct, labels = c("44","45","46","47","48","49","50","51","52","53","54","55"), common.legend = TRUE, legend = c("none"))

@@

```{r distance plot processing additional, message=FALSE, warning=FALSE, include=FALSE}
## July

@@

custom_labs_July <- c("32","33","34","35","36","37","338","39","40","41","42","43") #create custom labels and add them to dis_plot

@@

custom_labs_Oct <- c("44","45","46","47","48","49","50","51","52","53","54","55") #create custom labels and add them to dis_plot

@@

```{r distance plot additional, message=FALSE, warning=FALSE, echo=FALSE, fig.cap="Figure 10: Boxplots of total distance travelled by all particles from the release site over the course of the simulation for each scenario for July (winter) and October (spring). The x-axis represents the scenario number and the y-axis is the distance travelled in kilometers. The lower and upper hinges correspond to the first and third quartiles. The whiskers represent the range, solid black lines represent the median and black dots are outliers. The reader is referred to tables 1 and 2 for details pertaining to each scenario."}
